Диплом

### 2020-04-25 paper.tex
DHCP опции

@@

>>>>

\begin{figure}[H]
    \includegraphics[width=\textwidth / 2]{build/dhcp-simple.png}
    \caption{}
\end{figure}

@@

Реализация протокола DHCP в соответствии с RFC2131.
\begin{itemize}
    \item Прослушивание сети на наличие DHCP запросов.
    \item Присвоение настроек хоста на основе заданных администратором параметров.
    \item Отправка ответа с присвоенными настройками.
\end{itemize}

Поддержка следующих опций
\begin{description}
    \item[2] Time Offset
    \item[3] Router
    \item[4] Time server
    \item[5] Name server
    \item[6] Domain name server
    \item[7] Log server
    \item[8] Cookie server
    \item[9] LPR server
    \item[10] Impress server
    \item[11] Resource location server
    \item[12] Host name
    \item[13] Boot file size
    \item[14] Merit dump file
    \item[15] Domain name
    \item[16] Swap server
    \item[17] Root path
    \item[18] Extentions path
    \item[19] IP forwarding enable/disable
    \item[20] Non-local source routing enable/disable
    \item[21] Policy filter
    \item[22] Maximum datagram reassembly size
    \item[23] Default IP time to live
    \item[24] Path MTU aging timeout
    \item[25] Path MTU Plateau Table
    \item[26] Interface MTU
    \item[27] All subnets are local
    \item[28] Broadcast Address
    \item[29] Perform mask discovery
    \item[30] Mask supplier
    \item[31] Perform router discovery
    \item[32] Router solicitation address
    \item[33] Static route
    \item[34] Trailer encapsulation
    \item[35] ARP cache timeout
    \item[36] Ethernet encapsulation option
    \item[37] TCP default TTL
    \item[38] TCP keepalive interval
    \item[39] TCP keepalive garbage
    \item[40] Network Information service domain
    \item[41] Network Information servers
    \item[42] Network time protocol servers
    \item[43, 60] Vendor specific Information, Vendor class identifier
    \item[44] NetBIOS over TCP/IP name server
    \item[45] NetBIOS over TCP/IP datagram distribution server
    \item[46] NetBIOS over TCP/IP node type
    \item[47] NetBIOS over TCP/IP scope
    \item[48] X window system font server
    \item[49] X window system display manager
    \item[64] Network Information service+ domain
    \item[65] Network Information service+ servers
    \item[68] Mobile IP home agent
    \item[69] Simple Mail Transport Protocol (SMTP) server
    \item[70] Post Office Protocol (POP3) server
    \item[71] Network news Transport Protocol (NNTP) server
    \item[72] Default world wide web (www) server
    \item[73] Default finger server
    \item[74] Default Internet relay chat (IRC) server
    \item[75] StreetTalk Server
    \item[76] StreetTalk directory assistance (STDA) server
    \item[66] TFTP server name
    \item[67] Bootfile name
    \item[121] Classless route
    \item[118] Subnet selection
    \item[93, 94, 97] PXE options
\end{description}
